---
title: "Displacement Field HW"
output: html_notebook
---

```{r}
# Set the working directory.
setwd("~/Desktop/geologyGeometryAdvancedStructure")

# Load the necessary R libraries.
source("library/all.R")
library("ggplot2") # To install ggplot, type install.packages("ggplot2") into the console. 
library("gganimate") # to animate ggplots
library("gifski") # to render animated figures
library("magick") # for compositing GIFs
source("advancedStructureFunctions.R") # This is a companion file that contains some functions specifically written for this script. 
```


```{r}

# The velocity gradient tensor L is a tensor that describes the velocity (speed + direction) of all points in space. In this homework, we will use work with the 2D case, in which L is a 2x2 matrix. 

# L takes the form: 

#      | exDot    gammaDot |
# L =  | 0        -eyDot   |


#         Y
#         |
#         |
#         |
#         | 
# ————————|—————————— X
#         |
#         |
#         | 
#         |
     
# Below is an example of a velocity field
     
exDot = 0.05
gammaDot = 0
c = 0
eyDot = -exDot
     #-exDot #this is true if volume is perserved, i.e. the material is incompressible 

velGradTens = rbind(c(exDot, gammaDot),
                    c(c    ,    eyDot))

# Plot the 2D velocity gradient in (x,y) space

plot2DVelocityFieldFromL(exDot, gammaDot, 0, eyDot , gridSpacing = 2.5)


t = 10

if (exDot == 0) {
     
     posGradTens = rbind(c(exp(exDot*t), gammaDot * t          ),
                    c(0           , exp(eyDot*t)               )) 
     
} else {
          
     posGradTens = rbind(c(exp(exDot*t), gammaDot/exDot*sinh(exDot*t)),
                    c(0           , exp(eyDot*t)               ))
     
     }


plot2DCircleDisplacementFieldFromF(posGradTens[1,1], posGradTens[1,2], posGradTens[2,1], posGradTens[2,2])



#anim_save("GeneralShear.gif", animation=plot, height = 5, width = 10, units = "in", res = 150)

```

```{r}
plotParticles = plotParticlePaths(velGradTens, totalTime = t, numberOfIncrements = 100, gridSpacing = 2, superimposeStrain = FALSE, superimposeMaterialLine = FALSE, materialLineAngle = 45)

   
plotParticles

```



```{r}
plotParticlesAndStrain = plotParticlePaths(velGradTens, totalTime = t, numberOfIncrements = 100, gridSpacing = 2, superimposeStrain = TRUE, superimposeMaterialLine = FALSE, materialLineAngle = 45)

   
plotParticlesAndStrain[[1]]

plotParticlesAndStrain[[2]]
```


```{r}
plotParticlesStrainAndMaterial = plotParticlePaths(velGradTens, totalTime = t, numberOfIncrements = 100, gridSpacing = 2, superimposeStrain = TRUE, superimposeMaterialLine = TRUE, materialLineAngle = 150)

   
plotParticlesStrainAndMaterial[[1]]

plotParticlesStrainAndMaterial[[2]]

```


```{r}
# Make composit GIF

plot = plotParticlesStrainAndMaterial

aGIF = animate(plot[[1]], width =  920, height = 480) 

bGIF <- animate(plot[[2]], width = 480, height = 480)

a_mgif <- image_read(aGIF)
b_mgif <- image_read(bGIF)

new_gif <- image_append(c(a_mgif[1], b_mgif[1]))
for(i in 2:100){
  combined <- image_append(c(a_mgif[i], b_mgif[i]))
  new_gif <- c(new_gif, combined)
}

#new_gif

anim_save("GeneralShear_materialLine48deg.gif", animation=new_gif)
          
          
          #height = 5, width = 10, units = "in", res = 150)

```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

